%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\documentclass[10pt]{report}
\usepackage{fancyhdr}
\usepackage{xcolor}
\fontspec{[fontawesome-webfont.ttf]}
\usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Mukul Mehta}{
Sophomore @ Computer Science and Enginnering, IIT Kharagpur}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Indian Institute of \\ Technology Kharagpur}
\descript{B.Tech in Computer \\ Science and Engineering \\ CGPA: 8.83/10}
\location{2018-2022 | West Bengal, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INTEREST AREAS}
I'm an aspiring developer who's always looking out for interesting technical challenges. I'm intrigued by the idea of creating software and understanding \\ how real world systems work. \\~\\
I'm mainly interested in Backend engineering and designing systems/databases. \\~\\
I'm exploring areas of Distributed Systems, Computer Networks and Data Mining and I wish to pursue research in these areas. 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONTACT} 
\descript{RK Hall, \\ IIT Kharagpur,\\ West Bengal - 721302 \\ Phone: +91-76783 81645}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{LINKS} 
\faEnvelope\ {\href{mailto:mukul.csiitkgp@gmail.com}{ mukul.csiitkgp@gmail.com}}\\
\faGlobe\ {\href{https://mukul-mehta.github.io/}{ mukul-mehta.github.io}}\\
\faGithub\ {\href{https://github.com/mukul-mehta}{ mukul-mehta}}\\
\faLinkedinSquare\ {\href{https://www.linkedin.com/in/mukul-mehta12}{ mukul-mehta12}}\\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\emph{T - Theory | L - Laboratory}\\
\descript{Completed}
Programming \& Data Structures (T/L)\\
Discrete Structures (T)\\
Algorithms-1 (T/L) \\
\descript{Ongoing}
Software Engineering (T/L) \\
Formal Logic \& Automata Theory (T) \\
Switching Circuits \& Logic Design (T/L) \\
High Perf. Scientific Computing (T) \\ 
\descript{Online Courses}
\href{https://www.coursera.org/learn/machine-learning}{Machine Learning - Andrew Ng}\\
\href{https://online.codingblocks.com/courses/40}{ML - Coding Blocks (Ongoing)}\\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}

\runsubsection{RETROSPECTIVE ACCESS MANAGEMENT IN ONLINE ARCHIVES}
\descript{Under Prof. Mainack Mondal}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Investigating the effectiveness of tools which enable users to retrospectively modify privacy settings (Social Media or Cloud Storage).
\item Working on large-scale extraction of privacy settings \& profile data from Twitter \& Instagram to analyse patterns in privacy settings over time. 
\end{tightemize}

\sectionsep

\runsubsection{\href{https://github.com/iit-technology-ambit/Syphus}{IIT Technology Ambit}}
\descript{Backend Developer}
\location{Jun 2019 – Present }

\begin{tightemize}
\item IIT Technology Ambit is a tech magazine that covers innovation in tech across the IIT's, funded by the Dean, Sponsored Research and Industrial Consultancy, IIT Kharagpur.  
\item Part of a team building a REST based backend from scratch. I worked on writing DB Models, API Endpoints and unit tests.
\item The REST Structure was built using Flask-RESTPlus and used other frameworks such as Flask-Login and Sendgrid API for mailing.
\end{tightemize}
\sectionsep

\runsubsection{Path Planning and Kalman Filter}
\descript{AGV Task Round}
\begin{tightemize}
\item Optimized multiple data structures and pathfinding algorithms(Dijkstra and A*) to find a solution for a given maze, with multiple constraints towards emulating a real car. Implemented in C++ using OpenCV.
\item Implemented Kalman Filter for estimation and verification of uncertain observations by using Numpy, Matplotlib and OpenCV.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\begin{tabular}{r|p{15cm}}
\textsc{Programming Languages} & \textbf{ C | C++ | Python | JavaScript | GNU Octave (Familiar)} \\
\textsc{Libraries / Frameworks} & \textbf{Flask | Selenium | OpenCV | Numpy | sklearn | Snap.py }\\
\textsc{Databases} & \textbf{SQLAlchemy | MySQL | SQLite | MongoDB }\\
\textsc{Systems / Platforms} & \textbf{Git | Linux | Docker (Familiar) | Heroku | Nginx}\\ 
\textsc{Web Technolgies} & \textbf{HTML+CSS | REST | BeautifulSoup | Express (Familiar)
} \\
\end{tabular}
%----------------------------------------------------------------------------------------
%	Scholastic Achievements
%----------------------------------------------------------------------------------------

\section{SCHOLASTIC ACHIEVEMENTS}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item {\emph{Aditya Birla Scholarship}:} Among the top 35 students in the country and the 4 from IIT KGP to be nominated for the interviews in 2018.\\
\item{JEE Advanced \emph{AIR 215}:} Under top 0.15\% amongst more than 2,00,000 students \\
\item {JEE Main \emph{AIR 1584}:} In top 0.15\% amongst more than 12,00,000 students. \\
\end{tightemize}
\sectionsep

%	Activities and Leadership
%----------------------------------------------------------------------------------------

\section{Activities \& Leadership}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}


\item {\emph{Core Team Member, Kharagpur Open Source Society}:} Responsible for the smooth conduct of events to familiarize students with open source technologies and philosophy.\\
\item{\emph{Open Source Involvement:}} Part of gold-winning OpenSoft team of my hall(Project Litigator). Worked on multiple projects, hosted on GitHub. \\
\item{\emph{Tech Team, Gymkhana IIT Kharagpur}} Part of a team that is responsible for maintaining backend, student’s grievance portal etc, headed by the highest nominated technical position of the institute.

\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}\